make STEAM clear

### 2019-12-06 mstemc/index.tex
trivial modify the mstemc

% Intended LaTeX compiler: xelatex
\documentclass[koma,a4paper,utopia,10pt,listings-color,microtype,paralist,colorlinks]{org-article}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Set up the TikZ in Emacs Org Mode}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Set up the TikZ in Emacs Org Mode},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\begin{description}
An introduction on how to setup the TikZ environment in Emacs Org Mode.So that
in Org file, you can generate either vector graph of \texttt{pdf} format or raster
graph of \texttt{png} format. Furthermore, you can export the vector graph when latex
is called and otherwise raster graph.
\end{description}

\section{config the header args}
\label{sec:orgd6868d4}

@@

The example begins with several lines containing \texttt{\#+header} which is sort of
clutter. we can put them in a file and include it at the beginning of the Org
file.
\section{generate results with different formats}
\label{sec:org102d2b4}

By changing the extension of \texttt{:file} (which is \texttt{pdf} for
\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
body of the tikz code.
\section{export the results according to the backend}
\label{sec:org6c2af32}

@@

\section{the final workflow}
\label{sec:org7d290e8}

>>>>

% Intended LaTeX compiler: xelatex
\documentclass[koma,a4paper,utopia,10pt,listings-color,microtype,paralist,colorlinks]{org-article}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Set up the TikZ in Emacs Org File}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Set up the TikZ in Emacs Org File},
 pdfkeywords={},
 pdfsubject={An introduction to setup the TikZ environment in Emacs Org File.So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format. Furthermore, you can export the vector graph when latex is called and otherwise raster graph.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\hspace{0pt}\\

An introduction to setup the TikZ environment in Emacs Org File.So that in Org file, you can generate either vector graph of \texttt{pdf}  format or raster graph of \texttt{png} format. Furthermore, you can export the vector graph when latex is called and otherwise raster graph.

\section{config the header args}
\label{sec:org1e65b28}

@@

The example begins with several lines containing \texttt{\#+header} which is sort of
clutter. we can put them in a file and include it at the beginning of the Org
file.
\section{generate results with different formats}
\label{sec:org92aa971}

By changing the extension of \texttt{:file} (which is \texttt{pdf} for
\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
body of the tikz code.
\section{export the results according to the backend}
\label{sec:org8166ca3}

@@

\section{the final workflow}
\label{sec:org6fc731d}

### 2019-12-06 mstemc/mstemc.tex
trivial modify the mstemc

\section{Videos}
\label{sec:org23819b1}

\section{Posts}
\label{sec:orgb1ab608}

\section{Projects}
\label{sec:orge8d1fc9}

\subsection{my workflow of creating a video}
\label{sec:org8223223}
During the creation of one video, several tools are tuned to fit my workflow. In
this project several videos and posts will be created to make my workflow clear.

@@

\subsubsection{Emacs}
\label{sec:orgc041d09}

@@

\begin{enumerate}
\item program and debug
\label{sec:orgafa531d}

@@

\item Org mode - journalize your work
\label{sec:orge1afdea}

@@

\item Org mode - get things done
\label{sec:org11a73ef}

\item Org mode - write a diary
\label{sec:org58bfcb8}

\item Org mode - export your Org file
\label{sec:org4cc5d5b}

\item program and debug
\label{sec:org0a78023}

\item writing latex
\label{sec:orgdcebfa5}
\item org-journal
\label{sec:orgdb006ce}

@@

\item ox-hugo
\label{sec:orgefe2fb2}

@@

\item preview tikz picture in Org
\label{sec:org9816573}

@@

You can integrated TikZ code into the Org mode as a source block.A minimum
working example is shown as below.

[[file:~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png]]

\begin{center}
\includegraphics[width=0.4\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/tutorial.pdf}
\end{center}
\end{enumerate}

\subsubsection{Hugo}
\label{sec:org65579c9}

@@

\subsubsection{manim}
\label{sec:orgbb047b1}

\subsubsection{blender}
\label{sec:orge8838d0}

\section{Courses}
\label{sec:orgfc25921}
\end{document}

>>>>

\section{Videos}
\label{sec:org002a437}

\section{Posts}
\label{sec:org2d95323}

\subsection{Set up the TikZ in Emacs Org File}
\label{sec:org64c90ff}
\begin{summary}
Why is this in \textbf{green}?
\end{summary}

\subsubsection{config the header args}
\label{sec:org825d7de}

You can embed TiKz (One of \(\LaTeX\) graphic package) code into a Org file. With
org-babel, you can generate ,insert and export the figure generated from Tikz
package. At first, you need set up the environment. \href{https://orgmode.org/worg/org-contrib/babel/languages/ob-doc-LaTeX.html}{This Post} serves as a good
introduction for beginners. Following it you may have a minimum working example
like below:

\begin{verbatim}
#+name: tutorial
#+header: :file "~/Dropbox/mstemc_hugo/static/img/tikz/tutorial.png"
#+header: :results raw :exports none :fit yes :border 0cm
#+header: :imagemagick t :iminoptions -density 400 :imoutoptions -geometry 400 -flatten
#+header: :headers '("\\usepackage{tikz} \\usetikzlibrary{positioning, shapes.symbols, calc}")
#+begin_src latex
  \begin{tikzpicture}
    \node [circle, draw, fill=red!20] at (0,0) {1}
    child { node [circle, draw, fill=blue!30] {2}
      child { node [circle, draw, fill=green!30] {3} }
      child { node [circle, draw, fill=yellow!30] {4} }};
  \end{tikzpicture}
#+end_src
#+RESULTS: tutorial
[[file:../../img/tikz/tutorial.png]]
\end{verbatim}

The example begins with several lines containing \texttt{\#+header} which is sort of
clutter. we can put them in a file and include it at the beginning of the Org
file.
\subsubsection{generate results with different formats}
\label{sec:org75935d2}

By changing the extension of \texttt{:file} (which is \texttt{pdf} for
\texttt{"../../img/tikz/tutorial.pdf"} ), we can generate results with different formats.
Now, I need \texttt{pdf} and \texttt{png} . You can see the result by just press \texttt{C-c C-c} in the
body of the tikz code.
\subsubsection{export the results according to the backend}
\label{sec:org59da2c2}

You can set \texttt{:exports} to control how the results will be exported. Now I set it
as \texttt{none} which means the result will not be exported to latex or other format. I
want to set more options of the exports. So I use:

\begin{verbatim}
#+ATTR_HTML:  :width 800 :align center
#+ATTR_LATEX: :width 0.8\textwidth :align center
{{{if-latex(tutorial.pdf,tutorial.png)}}}
\end{verbatim}

\texttt{if-latex} is a Org MACRO whose definition is :
\begin{verbatim}
#+MACRO: if-latex (eval (if (org-export-derived-backend-p org-export-current-backend 'latex)
 (concat "[[file:../../img/tikz/"  $1 "]]")
 (concat "[[file:../../img/tikz/"  $2 "]]") ))
\end{verbatim}

The \texttt{if-latex} MACRO let you export different formats by the backend. If the
backend is \texttt{latex} then, \texttt{pdf} format figure will be exported. Otherwise, \texttt{png} format
figure. Eventually, in the final \texttt{pdf} document, you figure can be zoomed in or
out without losing any resolution.

\subsubsection{the final workflow}
\label{sec:orgc0cd8cc}

The minimum working example at the start of this post is simplifed as below.

\begin{verbatim}
#+header: :file  "../../img/tikz/tutorial.pdf"
#+begin_src latex
  \begin{tikzpicture}
    \node [circle, draw, fill=red!20] at (0,0) {1}
    child { node [circle, draw, fill=blue!30] {2}
      child { node [circle, draw, fill=green!30] {3} }
      child { node [circle, draw, fill=yellow!30] {4} }};
  \end{tikzpicture}
#+end_src

#+RESULTS:
[[file:../../img/tikz/tutorial.png]]

The following is the generated figure.
#+ATTR_HTML:  :width 800 :align center
#+ATTR_LATEX: :width 0.8\textwidth :align center
{{{if-latex(tutorial.pdf,tutorial.png)}}}
\end{verbatim}

Many settings are grouped into a setup file which is included at the top of this
post:
\begin{verbatim}
#+SETUPFILE: ~/.spacemacs.d/org-templates/math-en.org
\end{verbatim}

Now, If you set the extension of the target file in the first line either \texttt{pdf} or
\texttt{png} , a corresponding \texttt{pdf} or \texttt{png} figure will be generated. If execute \texttt{M-x
org-toggle-inline-images}  , you can preview the result. If export the org-file
as latex file then the \texttt{pdf} file, the image of \texttt{pdf} format will be inserted. If
export to other format, \texttt{png} image will be used.

\section{Projects}
\label{sec:org8f61cb8}

\subsection{my workflow of creating a video}
\label{sec:org597f5bb}
During the creation of one video, several tools are tuned to fit my workflow. In
this project several videos and posts will be created to make my workflow clear.

@@

\subsubsection{Emacs}
\label{sec:org76d34e1}

@@

\begin{enumerate}
\item program and debug
\label{sec:orgd2ab070}

@@

\item Org mode - journalize your work
\label{sec:org75ff6e1}

@@

\item Org mode - get things done
\label{sec:org4df4183}

\item Org mode - write a diary
\label{sec:org266bdcc}

\item Org mode - export your Org file
\label{sec:orge9ee370}

\item program and debug
\label{sec:orgcf10226}

\item writing latex
\label{sec:org69631c2}
\item org-journal
\label{sec:org06a8ebe}

@@

\item ox-hugo
\label{sec:orgde97df4}

@@

\item preview tikz picture in Org
\label{sec:org2bcb08b}

@@

You can integrated TikZ code into the Org mode as a source block. I have a
not-so-detailed post on how to set up the tikz environment in Org.
\end{enumerate}

\subsubsection{Hugo}
\label{sec:org79f095e}

@@

\subsubsection{manim}
\label{sec:orga490cc3}

\subsubsection{blender}
\label{sec:org362635d}

\section{Courses}
\label{sec:orgc9e6ff6}
\end{document}
